This chapter starts with a review of key previous work done in the domain of relaxed memory models.
We start by eliciting research works done in the design of memory models, coupled with works exposing problems due to ill defined or informally specified semantics. 
We then elicit research works done in the context of different memory models concerning validity of program transformations. 
Finally, we end with a list of tutorial works done in the axiomatic style specification of memory models.
\ \newline
\ \newline  
\hrule 
\ \newline 
\ \newline 

A lot of problems emerged with the introduction of concurrent computing. 
Starting with the famously known mutual exclusion problem way back in the 1960s introduced and solved by Djikstra et al.~\cite{Djikstra}, from it stemmed the ideas of semaphores and monitors that we all know today.  
Since then, a lot of well-known problems in concurrency such as The Producer Consumer Problem, Dining Philosopher's problem, Reader-Writer problem have come up, along with different algorithms to implement these in a practical sense, especially in Operating Systems. 

However, the above concerns in concurrency only revolves around the so-called ``critical section''; which requires that every thread trying to do something in a shared memory region must have exclusive access to it before doing anything. 
In recent decades, the need for more performance has increased; multiple hardwares having different features such as read-write buffers, caches, etc exist. 
Reliance solely on critical sections to perform operations on shared memory is today observed as a bottleneck. 
Without its use, however, the possible outcomes of a concurrent program increases and complicates the notion of \textit{atomicity} in actions done on shared memory.

\input{2.Background/2.MemoryConsistencyModels.tex}

\input{2.Background/3.OptimizationsUnderWeakMem.tex}

\input{2.Background/4.AxiomaticSpecWeakMem.tex}
  
\input{2.Background/5.OtherConcernsWithModel.tex}

\ \newline
\ \newline  
\hrule 
\ \newline 
\ \newline 
As a summary, this chapter elicited the key research works done in the domain of relaxed memory models, its specification and its impact of program transformations. 
In the next chapter, we state the problems in the existing specification of the ECMAScript memory model, followed by a more formal specification of the same.