\section{From Candidates to Program}

    So far we have only addressed reordering at the Candidate level. 
    In practice, a program can have many Candidates. 
    This is due to the program having several conditional branches and loops. 
    To analyze when we can reorder two events at the program level, we must also address the involvement of conditionals and loops that may be between these two events.
    But locally asserting why a particular reordering is valid is non-trivial to understand. 
    The compiler does global level optimizations that involve several local transformations that may include reordering. 
    In addition, the previous proofs show us that we mainly are interested in identifying whether a reordering introduces new observables, not with why such a reordering would be effective for performance.

    Hence, the way we approach this is to not have any assumptions as to why the compiler chooses to do a particular reordering. 
    Instead, we only check if the reordered program can have its observable behaviors as a subset of the original. 
    This ensures that we do not concern ourselves with the algorithm behind the compiler optimization. 
    Such an approach makes reordering parametric to the memory model. 
    The downside is that this approach will be conservative as we use no information as to why a particular set of events are reordered. 
    We do not compare and contrast in details the perks of both approaches. 
    This is beyond the scope of this thesis.

    We assume that conditionals do not have break/continue-like semantics. 
    We assume that loops have the following properties:
    \begin{itemize}
        \item Iterate at least once in an execution of the program.
        \item Are finite (loops terminate).
        \item Entry is only from the start of the loop body or from the end of the loop body (no goto/continue/break-like semantics).
        \item Exit is only from the end of loop body. 
    \end{itemize}

    We first define two properties that relate conditionals to Candidates of a program.
    We then use these properties to state a lemma which will be useful to prove the corollary that follows which establishes the condition under which reordering in programs with conditionals is safe. 
    
    \input{4.InstructionReordering/5.ValidReorderingProgram/conditionals.tex}

    In addition to the above proof, we also show certain counter examples where reordering in the presence of conditionals may not be safe to do. 
    This facilitates better understanding of the proof and its arguments. 
    These counter examples are with respect to reordering of writes. 
    These examples are in Appendix A.2.

    \input{4.InstructionReordering/5.ValidReorderingProgram/loops.tex}