This chapter starts with exposing some problems with the existing specifications of the model. 
The latter part introduces the key components of the model that we find essential to address program transformations. 
We start by introducing Agents and Event sets, followed by various Binary Relations defined between events. 
We then introduce certain helper definitions that prove useful in understanding the Axioms of the model. 
We then use the binary relations and definitions to specify the Axioms of the model.
Lastly, we define Races followed by defining what a Consistent Execution is as per the specification of the model.  
\ \newline
\ \newline  
\hrule 
\ \newline 
\ \newline 

\input{4.ECMAScriptMemoryModel/0.Intro.tex}

\input{4.ECMAScriptMemoryModel/1.Agents.tex}

\input{4.ECMAScriptMemoryModel/2.Event_Sets.tex}

\input{4.ECMAScriptMemoryModel/3.Event_Relations.tex}

\input{4.ECMAScriptMemoryModel/4.Ordering_Relations_On_Events.tex}

\input{4.ECMAScriptMemoryModel/5.PreliminaryDefinitions.tex}

\input{4.ECMAScriptMemoryModel/6.Valid_Execution_Rules.tex}

\input{4.ECMAScriptMemoryModel/7.Race.tex}

\input{4.ECMAScriptMemoryModel/8.Valid_Execution.tex}

\ \newline
\ \newline  
\hrule 
\ \newline 
\ \newline 
As a summary, this chapter axiomatically defined the ECMAScript memory model. 
The model is defined using binary relations on events and specifying the constraints of the model in terms of restricting reads-from relations given other binary relations that can exist between events in a Candidate Execution.
In the next chapter, we use this formal model to reason about the validity of instruction reordering under the constraints of the model.