%Races----------------------------------------------------------------------------------------------------------------------------------     
    \section{Race}

        We would want our concurrent programs to be written in such a way that the order in which shared memory is read from or written to is deterministic.
        This, however, may not always be the case. 
        For applications such as client-server interactions, we would rather be more comfortable keeping the client requests being serviced in a non-deterministic fashion. 
        This is because clients can be in millions, and always having a fixed order in which they should be serviced may not be ideal.
        The accesses to shared memory that are involved, which need to be deterministically ordered, but are left to program execution, are said to \textit{race} and are in a \textit{race condition}.
        Pairs of accesses that need to be ordered are those whose order affects the final outcome (observable behavior) of the program.
        In our view, they are simply those pairs, of which at least one of them is a write. 
        
        In the context of relaxed memory accesses, another type of race exists.
        In the normal \textit{race condition}, though accesses are not ordered deterministically by us, every execution will give us an outcome that can be justified using one particular order in which the concurrent accesses were issued. 
        However, there could be cases, i.e. outcomes of program execution, where no ordering among these accesses can justify\footnotemark.
        In such a situation, concurrent accesses are said to have a \textit{data race} among them.    
        
        \footnotetext{This is attributed to the notion of \textit{atomicity}. Atomic accesses, ensure that only the outcomes that result due to their different orderings are possible. Other accesses that do not respect this rule are called \textit{non-atomic}. In the context of our model, they are considered to be of type $uo$.}

        We define the two forms of races formally with respect to the ECMAScript memory model.
        
        \subsection{Race Condition $RC$} 
            We define \set{RC} as the set of all pairs of events that are in a race. 
            Two events $e$ and $d$ are in a race when they are shared memory events:
            \begin{align*}
                (e \in SM)\ \wedge\ (d \in SM).
            \end{align*}
            having overlapping or equal ranges, not ordered by the $\stck{_\textit{hb}}$ relation with each other, and which are either two writes or the two events are involved in a $\stck{_\textit{rf}}$ relation with each other. 
            This can be stated concisely as,
            \begin{align*}
                \neg \ (\reln{e}{hb}{d})\ \wedge\ \neg \ (\reln{d}{hb}{e}) 
                \ \wedge \ 
                (
                (\event{e,d}{W}\  \wedge\ (\Re(d) \cap_{\Re} \Re(e) \neq \phi)) 
                    \  \vee\ (d \stck{_\textit{rf}} e)\ \vee\ (e \stck{_\textit{rf}} d)
                ).
            \end{align*}
                    
        \subsection{Data Race $DR$} 
            We define \set{DR} as the set of all pairs of events that are in a data-race. 
            Two events are in a data race when they are already in a race condition and when the two events are not both of type \textit{sc}, or they have overlapping ranges. 
            This is concisely stated as:  
            \begin{align*}
                \event{e,d}{RC}  \ \wedge \ 
                ((\neg\et{e}{sc} \ \vee \ \neg\et{d}{sc}) \ \vee \ 
                (\Re(e) \cap_{\Re} \Re(d) \neq \Re(e) \cup_{\Re} \Re(d))). 
            \end{align*}
            
        \paragraph{Data-Race-Free (DRF) Programs}
            An execution is considered data-race-free if none of the above conditions for \textit{data-race} occur among events in a candidate execution and its observable behaviors. 
            A program is data-race-free if all its executions are data-race-free.          
            \textit{The memory model guarantees Sequential Consistency for all data-race free programs (SC-DRF).}      