There are countless people who have influenced me through these years and have motivated me to keep doing this thesis.
Unfortunately, I cannot mention all of their names due to space constraints as well as the fact that I may not know their influence on me yet.
However, I do want to mention a few important names of people that have in my eyes influenced me the most. 
Firstly, my advisor Professor Clark Verbrugge.
Having not done any rigorous theoretical work or research before and yet wanting to do a theoretical one as a thesis, he gave me high level guidelines to ground me and to keep me from being overwhelmed from framing my own theorems, lemmas, proofs, etc. 
I would not have gotten a better advisor than him, especially during the initial years when I was trying to build an intuitive foundation. 
Also, to advise someone in this sense is quite a challenge in my eyes.
Secondly, my friend, Aarti Kashyap, mainly for being a patient listener, a motivator that made me attend several conferences and for always giving constructive feedback. 
I needed an outside perspective and somebody to discuss with about various aspects of this research at any time; and she being there for it has helped me shape ideas of this thesis better. 
Thirdly, Conrad Watt, mainly for giving me an inside perspective of this topic of research and motivating me to pursue this thesis topic.
Lastly, my family, friends and lab-mates, who always assured me the support (mentally or otherwise) I would need at any time during my masters. 
I would like to also thank Viktor Vafeiadis, my internship advisor, who helped me look at the research I did all this while in a simplistic way.
This has in some way reflected the way I write or present my research ideas.
Finally, God, for guiding me in his/her own way and presenting me with ample opportunities to grow as a human being as well as a researcher these years.